---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Linear regression

<!-- badges: start -->
[![R-CMD-check](https://github.com/xinyozha/homework3/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/xinyozha/homework3/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/xinyozha/homework3/branch/main/graph/badge.svg)](https://app.codecov.io/gh/xinyozha/homework3?branch=main)
<!-- badges: end -->

The goal of this R package is set a Linear regression function (my_lm) to find some basic information such as point estimate, fitted.values, residuals, mse, rsquared, adj_rsquared, standard error of beta, t.statistic, p.value, F.statistic, df1 and df2. 

## Installation

You can install the development version of homework3 (Linear regression) from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("xinyozha/homework3")
```

## Loading packages

```{r example}
library(homework3)
```

Use the following code to find more details about the "homework3" package (Linear regression):

```{r}
browseVignettes("homework3")
```


