---
title: "my-vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{my-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


```{r setup}
library(bench)
```



### Basic command

To fit the linear regression model using 'homework3' package, generally two input needs to be prepared 

* **formula**: A formula of linear regression such as y ~ x1 + x2.

* **data**: The dataset we want to analyses.

Some other parameters are needed for `my_confint`:

For `my_confint`, parameter `level` is needed:

* **level**: numerical value, the significance of the CI, default = 0.95.

### Loading packages

```{r}
library(homework3)
```

### Set some data example and the result of `stats::lm` in `R` and `my linear regression`.

```{r}
data <- mtcars
formula <- mpg ~ disp + hp
m1 <- lm(formula, data)
s_m1 <- summary(m1)
m2 <- my_lm(formula, data)
```

### Some examples of using `my_lm` function and `my_confint` function.
*(1) Calculate the coefficients: 
```{r}
my_lm(formula, data)$coefficients
```
*(2) Calculate the residuals: 
```{r}
my_lm(formula, data)$residuals
```

*(3) Calculate the estimate value: 
```{r}
my_lm(formula, data)$fitted.values
```
*(4) Calculate the sigma square: 
```{r}
my_lm(formula, data)$mse
```

*(5) Calculate the R squared: 
```{r}
my_lm(formula, data)$rsquared
```
*(6) Calculate the Confidence Interval:
```{r}
CI = my_confint(formula, data, 0.95)
```

*(7) Calculate the F statistic:
```{r}
ff <- c(
  my_lm(formula, data)$F_stat, my_lm(formula, data)$df1,
  my_lm(formula, data)$df2
)
```

Using other items are as same as above.

## Correctness
(1)Test the coefficients.
```{r}
all.equal(as.numeric(my_lm(formula, data)$coefficients), 
          as.numeric(m1$coefficients))
```
(2)Test the residuals
```{r}
all.equal(as.numeric(my_lm(formula, data)$residuals), 
          as.numeric(m1$residuals))
```
(3)Test the fitted values
```{r}
all.equal(as.numeric(my_lm(formula, data)$fitted.values), 
          as.numeric(m1$fitted.values))
```
(4)Test the MSE
```{r}
all.equal(as.numeric(my_lm(formula, data)$mse), 
          as.numeric(s_m1$sigma^2))
```
(5)Test the R square and adj_R square
```{r}
all.equal(as.numeric(my_lm(formula, data)$rsquared), 
          as.numeric(s_m1$r.squared))
all.equal(as.numeric(my_lm(formula, data)$adj_rsquared), 
          as.numeric(s_m1$adj.r.squared))
```
(6)Test the CI
```{r}
all.equal(as.numeric(my_confint(formula, data, 0.95)), 
          as.numeric(confint(m1)))
```
(7)Test the F statistic
```{r}
all.equal(ff, as.numeric(s_m1$fstatistic))
```
Testing other items are as same as above.

### Efficiency
Compare the itr_per_sec between `stats::lm` in `R` and my linear regression `my_lm` function by using `bench:mark()` function (coefficients):
```{r}
code_efficiency_comparison_lm <- bench::mark("homework3::my_lm()" = {
  beta_actual <- m2$coefficients
  as.vector(beta_actual)
}, "lm" = {
  beta_expected <- m1$coefficients
  as.vector(beta_expected)
})
summary(code_efficiency_comparison_lm)
itr_per_sec <- as.numeric(code_efficiency_comparison_lm[[4]])
itr_per_sec_ratio <- itr_per_sec[1] / itr_per_sec[2]
```
From the results of `bench::mark`, it can be seen that `my_lm` is about `r round(itr_per_sec_ratio, digits = 4)` times as faster as `stats:lm`.

Next, comparing the speed of constructing confidence interval `my_confint`:

```{r}
code_efficiency_comparison_CI <- bench::mark("homework3::my_confint()" = {
  unname(CI_actual <- CI)
}, "confint" = {
  unname(CI_expected <- confint(m1))
})
summary(code_efficiency_comparison_CI)
itr_per_sec <- as.numeric(code_efficiency_comparison_CI[[4]])
itr_per_sec_ratio <- itr_per_sec[1] / itr_per_sec[2]
```
From the results of `bench::mark`, it can be seen that `my_confint` is about `r round(itr_per_sec_ratio, digits = 4)` times as faster as `stats:lm`.




